Satellite Constellation Avoidance with the Rubin Observatory Legacy Survey of Space and Time

### 2022-11-28 for_ph/ms.tex
ph version

\begin{figure*}[ht!]
\epsscale{0.37}
\plotone{plots/starlink_tles_v1_0.00_basisfunc.pdf}
\plotone{plots/starlink_tles_v2_0.00_basisfunc.pdf}
\plotone{plots/oneweb_tles_0.00_basisfunc.pdf}
\epsscale{1}
\caption{Satellite avoidance maps constructed for the Rubin scheduler for each simulated constellation. Each is for a twilight observation period of 90 minutes (beginning after sunset with a Sun altitude of $-17.1$ degrees). The map projections are rotated so zenith is in the center of the image. Darker regions have more illuminated satellites and therefore more negative weighting. By varying the dodging weight placed on these maps, the scheduler will more actively avoid regions of the sky where satellites could streak images.
%\vspace{3em}
\label{fig-simulated-scheduler}
}
\end{figure*}

@@

\bibliography{ms}{}
\bibliographystyle{aasjournal}

>>>>

\begin{figure*}[ht!]
\epsscale{0.37}
\plotone{plots/starlink_tles_v1_0_00_basisfunc.pdf}
\plotone{plots/starlink_tles_v2_0_00_basisfunc.pdf}
\plotone{plots/oneweb_tles_0_00_basisfunc.pdf}
\epsscale{1}
\caption{Satellite avoidance maps constructed for the Rubin scheduler for each simulated constellation. Each is for a twilight observation period of 90 minutes (beginning after sunset with a Sun altitude of $-17.1$ degrees). The map projections are rotated so zenith is in the center of the image. Darker regions have more illuminated satellites and therefore more negative weighting. By varying the dodging weight placed on these maps, the scheduler will more actively avoid regions of the sky where satellites could streak images.
%\vspace{3em}
\label{fig-simulated-scheduler}
}
\end{figure*}

@@

\bibliographystyle{aasjournal}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\href{#1}{#1}}
\providecommand{\dodoi}[1]{doi:~\href{http://doi.org/#1}{\nolinkurl{#1}}}
\providecommand{\doeprint}[1]{\href{http://ascl.net/#1}{\nolinkurl{http://ascl.net/#1}}}
\providecommand{\doarXiv}[1]{\href{https://arxiv.org/abs/#1}{\nolinkurl{https://arxiv.org/abs/#1}}}

\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy2013}
{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
  \aap, 558, A33, \dodoi{10.1051/0004-6361/201322068}

\bibitem[{{Astropy Collaboration} {et~al.}(2018){Astropy Collaboration},
  {Price-Whelan}, {Sip{\H{o}}cz}, {G{\"u}nther}, {Lim}, {Crawford}, {Conseil},
  {Shupe}, {Craig}, {Dencheva}, {Ginsburg}, {VanderPlas}, {Bradley},
  {P{\'e}rez-Su{\'a}rez}, {de Val-Borro}, {Aldcroft}, {Cruz}, {Robitaille},
  {Tollerud}, {Ardelean}, {Babej}, {Bach}, {Bachetti}, {Bakanov}, {Bamford},
  {Barentsen}, {Barmby}, {Baumbach}, {Berry}, {Biscani}, {Boquien}, {Bostroem},
  {Bouma}, {Brammer}, {Bray}, {Breytenbach}, {Buddelmeijer}, {Burke},
  {Calderone}, {Cano Rodr{\'\i}guez}, {Cara}, {Cardoso}, {Cheedella}, {Copin},
  {Corrales}, {Crichton}, {D'Avella}, {Deil}, {Depagne}, {Dietrich}, {Donath},
  {Droettboom}, {Earl}, {Erben}, {Fabbro}, {Ferreira}, {Finethy}, {Fox},
  {Garrison}, {Gibbons}, {Goldstein}, {Gommers}, {Greco}, {Greenfield},
  {Groener}, {Grollier}, {Hagen}, {Hirst}, {Homeier}, {Horton}, {Hosseinzadeh},
  {Hu}, {Hunkeler}, {Ivezi{\'c}}, {Jain}, {Jenness}, {Kanarek}, {Kendrew},
  {Kern}, {Kerzendorf}, {Khvalko}, {King}, {Kirkby}, {Kulkarni}, {Kumar},
  {Lee}, {Lenz}, {Littlefair}, {Ma}, {Macleod}, {Mastropietro}, {McCully},
  {Montagnac}, {Morris}, {Mueller}, {Mumford}, {Muna}, {Murphy}, {Nelson},
  {Nguyen}, {Ninan}, {N{\"o}the}, {Ogaz}, {Oh}, {Parejko}, {Parley}, {Pascual},
  {Patil}, {Patil}, {Plunkett}, {Prochaska}, {Rastogi}, {Reddy Janga},
  {Sabater}, {Sakurikar}, {Seifert}, {Sherbert}, {Sherwood-Taylor}, {Shih},
  {Sick}, {Silbiger}, {Singanamalla}, {Singer}, {Sladen}, {Sooley},
  {Sornarajah}, {Streicher}, {Teuben}, {Thomas}, {Tremblay}, {Turner},
  {Terr{\'o}n}, {van Kerkwijk}, {de la Vega}, {Watkins}, {Weaver}, {Whitmore},
  {Woillez}, {Zabalza}, \& {Astropy Contributors}}]{astropy2018}
{Astropy Collaboration}, {Price-Whelan}, A.~M., {Sip{\H{o}}cz}, B.~M., {et~al.}
  2018, \aj, 156, 123, \dodoi{10.3847/1538-3881/aabc4f}

\bibitem[{{Astropy Collaboration} {et~al.}(2022){Astropy Collaboration},
  {Price-Whelan}, {Lim}, {Earl}, {Starkman}, {Bradley}, {Shupe}, {Patil},
  {Corrales}, {Brasseur}, {N{\"o}the}, {Donath}, {Tollerud}, {Morris},
  {Ginsburg}, {Vaher}, {Weaver}, {Tocknell}, {Jamieson}, {van Kerkwijk},
  {Robitaille}, {Merry}, {Bachetti}, {G{\"u}nther}, {Aldcroft},
  {Alvarado-Montes}, {Archibald}, {B{\'o}di}, {Bapat}, {Barentsen},
  {Baz{\'a}n}, {Biswas}, {Boquien}, {Burke}, {Cara}, {Cara}, {Conroy},
  {Conseil}, {Craig}, {Cross}, {Cruz}, {D'Eugenio}, {Dencheva}, {Devillepoix},
  {Dietrich}, {Eigenbrot}, {Erben}, {Ferreira}, {Foreman-Mackey}, {Fox},
  {Freij}, {Garg}, {Geda}, {Glattly}, {Gondhalekar}, {Gordon}, {Grant},
  {Greenfield}, {Groener}, {Guest}, {Gurovich}, {Handberg}, {Hart},
  {Hatfield-Dodds}, {Homeier}, {Hosseinzadeh}, {Jenness}, {Jones}, {Joseph},
  {Kalmbach}, {Karamehmetoglu}, {Ka{\l}uszy{\'n}ski}, {Kelley}, {Kern},
  {Kerzendorf}, {Koch}, {Kulumani}, {Lee}, {Ly}, {Ma}, {MacBride}, {Maljaars},
  {Muna}, {Murphy}, {Norman}, {O'Steen}, {Oman}, {Pacifici}, {Pascual},
  {Pascual-Granado}, {Patil}, {Perren}, {Pickering}, {Rastogi}, {Roulston},
  {Ryan}, {Rykoff}, {Sabater}, {Sakurikar}, {Salgado}, {Sanghi}, {Saunders},
  {Savchenko}, {Schwardt}, {Seifert-Eckert}, {Shih}, {Jain}, {Shukla}, {Sick},
  {Simpson}, {Singanamalla}, {Singer}, {Singhal}, {Sinha}, {Sip{\H{o}}cz},
  {Spitler}, {Stansby}, {Streicher}, {{\v{S}}umak}, {Swinbank}, {Taranu},
  {Tewary}, {Tremblay}, {Val-Borro}, {Van Kooten}, {Vasovi{\'c}}, {Verma}, {de
  Miranda Cardoso}, {Williams}, {Wilson}, {Winkel}, {Wood-Vasey}, {Xue},
  {Yoachim}, {Zhang}, {Zonca}, \& {Astropy Project Contributors}}]{astropy2022}
{Astropy Collaboration}, {Price-Whelan}, A.~M., {Lim}, P.~L., {et~al.} 2022,
  \apj, 935, 167, \dodoi{10.3847/1538-4357/ac7c74}

\bibitem[{Gillies {et~al.}(2007--)}]{shapely2007}
Gillies, S., {et~al.} 2007--, Shapely: manipulation and analysis of geometric
  objects.
\newblock \url{https://github.com/Toblerity/Shapely}

\bibitem[{{G{\'o}rski} {et~al.}(2005){G{\'o}rski}, {Hivon}, {Banday},
  {Wandelt}, {Hansen}, {Reinecke}, \& {Bartelmann}}]{healpix2005}
{G{\'o}rski}, K.~M., {Hivon}, E., {Banday}, A.~J., {et~al.} 2005, \apj, 622,
  759, \dodoi{10.1086/427976}

\bibitem[{{Halferty} {et~al.}(2022){Halferty}, {Reddy}, {Campbell}, {Battle},
  \& {Furfaro}}]{Halferty2022}
{Halferty}, G., {Reddy}, V., {Campbell}, T., {Battle}, A., \& {Furfaro}, R.
  2022, \mnras, 516, 1502, \dodoi{10.1093/mnras/stac2080}

\bibitem[{{Hall} {et~al.}(2021){Hall}, {Walker}, {Rawls}, {McDowell}, {Seaman},
  {Venkatesan}, {Lowenthal}, {Green}, {Krafton}, \& {Parriott}}]{satcon2}
{Hall}, J., {Walker}, C., {Rawls}, M., {et~al.} 2021, in Bulletin of the
  American Astronomical Society, 2.205, \dodoi{10.3847/25c2cfeb.4554c01f}

\bibitem[{Harris {et~al.}(2020)Harris, Millman, van~der Walt, Gommers,
  Virtanen, Cournapeau, Wieser, Taylor, Berg, Smith, Kern, Picus, Hoyer, van
  Kerkwijk, Brett, Haldane, del R{\'{i}}o, Wiebe, Peterson,
  G{\'{e}}rard-Marchant, Sheppard, Reddy, Weckesser, Abbasi, Gohlke, \&
  Oliphant}]{harris2020array}
Harris, C.~R., Millman, K.~J., van~der Walt, S.~J., {et~al.} 2020, Nature, 585,
  357, \dodoi{10.1038/s41586-020-2649-2}

\bibitem[{{Hasan} {et~al.}(2022){Hasan}, {Tyson}, {Saunders}, \&
  {Xin}}]{hasan22}
{Hasan}, I., {Tyson}, J.~A., {Saunders}, C., \& {Xin}, B. 2022, Astronomy and
  Computing, 39, 100584, \dodoi{10.1016/j.ascom.2022.100584}

\bibitem[{Hunter(2007)}]{Hunter:2007}
Hunter, J.~D. 2007, Computing in Science \& Engineering, 9, 90,
  \dodoi{10.1109/MCSE.2007.55}

\bibitem[{{Ivezi{\'c}} {et~al.}(2019){Ivezi{\'c}}, {Kahn}, {Tyson}, {Abel},
  {Acosta}, {Allsman}, {Alonso}, {AlSayyad}, {Anderson}, {Andrew}, \&
  et~al.}]{overview}
{Ivezi{\'c}}, {\v Z}., {Kahn}, S.~M., {Tyson}, J.~A., {et~al.} 2019, \apj, 873,
  111, \dodoi{10.3847/1538-4357/ab042c}

\bibitem[{{Lawrence} {et~al.}(2022){Lawrence}, {Rawls}, {Jah}, {Boley}, {Di
  Vruno}, {Garrington}, {Kramer}, {Lawler}, {Lowenthal}, {McDowell}, \&
  {McCaughrean}}]{lawrence22}
{Lawrence}, A., {Rawls}, M.~L., {Jah}, M., {et~al.} 2022, Nature Astronomy, 6,
  428, \dodoi{10.1038/s41550-022-01655-6}

\bibitem[{{Naghib} {et~al.}(2019){Naghib}, {Yoachim}, {Vanderbei}, {Connolly},
  \& {Jones}}]{naghib19}
{Naghib}, E., {Yoachim}, P., {Vanderbei}, R.~J., {Connolly}, A.~J., \& {Jones},
  R.~L. 2019, \aj, 157, 151, \dodoi{10.3847/1538-3881/aafece}

\bibitem[{{Rhodes}(2019)}]{Rhodes2019}
{Rhodes}, B. 2019, {Skyfield: High precision research-grade positions for
  planets and Earth satellites generator}, Astrophysics Source Code Library,
  record ascl:1907.024.
\newblock \doeprint{1907.024}

\bibitem[{{Tyson} {et~al.}(2020){Tyson}, {Ivezi{\'c}}, {Bradshaw}, {Rawls},
  {Xin}, {Yoachim}, {Parejko}, {Greene}, {Sholl}, {Abbott}, \&
  {Polin}}]{tyson20}
{Tyson}, J.~A., {Ivezi{\'c}}, {\v{Z}}., {Bradshaw}, A., {et~al.} 2020, \aj,
  160, 226, \dodoi{10.3847/1538-3881/abba3e}

\bibitem[{Virtanen {et~al.}(2020)Virtanen, Gommers, Oliphant, Haberland, Reddy,
  Cournapeau, Burovski, Peterson, Weckesser, Bright, {van der Walt}, Brett,
  Wilson, Millman, Mayorov, Nelson, Jones, Kern, Larson, Carey, Polat, Feng,
  Moore, {VanderPlas}, Laxalde, Perktold, Cimrman, Henriksen, Quintero, Harris,
  Archibald, Ribeiro, Pedregosa, {van Mulbregt}, \& {SciPy 1.0
  Contributors}}]{2020SciPy-NMeth}
Virtanen, P., Gommers, R., Oliphant, T.~E., {et~al.} 2020, Nature Methods, 17,
  261, \dodoi{10.1038/s41592-019-0686-2}

\bibitem[{{Walker} {et~al.}(2020{\natexlab{a}}){Walker}, {Hall}, {Allen},
  {Green}, {Seitzer}, {Tyson}, {Bauer}, {Krafton}, {Lowenthal}, {Parriott},
  {Puxley}, {Abbott}, {Bakos}, {Barentine}, {Bassa}, {Blakeslee}, {Bradshaw},
  {Cooke}, {Devost}, {Galad{\'\i}-Enr{\'\i}quez}, {Haase}, {Hainaut},
  {Heathcote}, {Jah}, {Krantz}, {Kucharski}, {McDowell}, {Mr{\'o}z}, {Otarola},
  {Pearce}, {Rawls}, {Saunders}, {Seaman}, {Siminski}, {Snyder},
  {Storrie-Lombardi}, {Tregloan-Reed}, {Wainscoat}, {Williams}, \&
  {Yoachim}}]{satcon1}
{Walker}, C., {Hall}, J., {Allen}, L., {et~al.} 2020{\natexlab{a}}, in Bulletin
  of the American Astronomical Society, Vol.~52, 0206,
  \dodoi{10.3847/25c2cfeb.346793b8}

\bibitem[{{Walker} {et~al.}(2020{\natexlab{b}}){Walker}, {Di Pippo},
  {Aub{\'e}}, {Barentine}, {Benkhaldoun}, {Benvenuti}, {Bouroussis}, {Green},
  {Hearnshaw}, {Mackenzie}, {Liszt}, {Lowenthal}, {Mu{\~n}oz-Tu{\~n}{\'o}n},
  {Nield}, {Ricard}, {Rodriguez Espinosa}, {Sanhueza}, {Varela P{\'e}rez},
  {Williams}, {Lau}, {Mu{\~n}oz Tu{\~n}{\'o}n}, {Rodr{\'\i}guez Espinosa},
  {Mu{\~n}oz-Tu{\~n}on}, {Armas}, {Benn}, {Blattner}, {Diaz-Castro}, {Donners},
  {Douglas}, {Ga{\v{s}}parovsk{\'y}}, {Hall}, {Koll{\'a}th}, {Novak},
  {Ortolani}, {Rodr{\'\i}guez Espinosa}, {Lowenthal}, {Bara}, {J{\"a}gerbrand},
  {Jechow}, {Longcore}, {Motta}, {Schlangen}, {Schroer}, {Lucatello},
  {Galad{\'\i}-Enr{\'\i}quez}, {Micheva}, {Otarola}, {Allen}, {Bannister},
  {Barstow}, {Bassa}, {Davies}, {Devost}, {Hainaut}, {Jah}, {Krafton},
  {Krantz}, {Kucharski}, {Maclay}, {Massey}, {Mudd}, {McDowell}, {Parriott},
  {Pearce}, {Rawls}, {Rotola}, {Seaman}, {Seitzer}, {Siminski},
  {Storrie-Lombardi}, {Street}, {Tregloan-Reed}, {Tyson}, {Unda-Sanzana},
  {Wainscoat}, \& {Zamora}}]{dqs1}
{Walker}, C., {Di Pippo}, S., {Aub{\'e}}, M., {et~al.} 2020{\natexlab{b}},
  {Dark \& Quiet Skies I (2020)}, Dark \& Quiet Skies I (2020), Report of the
  conference held 5-9 October, 2020., \dodoi{10.5281/zenodo.5898785}

\bibitem[{{Walker} {et~al.}(2021){Walker}, {Di Pippo}, {Aub{\'e}}, {Barentine},
  {Benkhaldoun}, {Benvenuti}, {Bouroussis}, {Di Vruno}, {Green}, {Hearnshaw},
  {Aoraki}, {Liszt}, {Lowenthal}, {Mu{\~n}oz-Tu{\~n}{\'o}n}, {Nield}, {Ohishi},
  {Ricard}, {Rodriguez Espinosa}, {Rotola}, {Sanhueza}, {Var{\'e}la P{\'e}rez},
  {Williams}, {Cameron}, {H{\"a}nel}, {Hartley}, {Krop-Benesch}, {Lien},
  {Motta}, {Ribas}, {Rol}, {Yakushina}, {Zielinska-Dabkowska}, {Zhao},
  {Aganaba}, {Boley}, {Cirkovic}, {Falle}, {Freeland}, {Hallet}, {Hanlon},
  {Jakhu}, {Jamschon MacGarry}, {Johnson}, {Kazlouskaya}, {Martin},
  {Masson-Zwaan}, {Mishra}, {Moro-Aguilar}, {Mudd}, {Simon-Butler}, {Van Eijk},
  {Venn}, {Wager}, {Alis}, {Berry}, {Bharadwaj}, {Davis}, {Lagadec}, {Le
  Breuilly}, {Lucatello}, {Massey}, {Parriott}, {Valdivia}, {Weeden}, {Hofer},
  {Andrade}, {Askari}, {Baruch}, {Bohnlein}, {Dunn}, {Grunsfeld}, {Jansson},
  {Knox}, {Raval}, {Sedwick}, {Smith}, {Vanotti}, {Bassa}, {Cui}, {Galadi},
  {Hainaut}, {Hasan}, {K{\'e}b{\'e}}, {Lawler}, {McDowell}, {Otarola}, {Rawls},
  {Seitzer}, {Street}, {Pree}, {Gergely}, {Hellbourg}, {Indermuehle},
  {Lindqvist}, {Tzioumis}, {Vanderley}, {Winkel}, \& {Zhang}}]{dqs2}
---. 2021, {Dark \& Quiet Skies II (2021)}, Dark \& Quiet Skies II (2021),
  Report of the conference held 3-7 October, 2021.,
  \dodoi{10.5281/zenodo.5874725}

\bibitem[{Yoachim {et~al.}(2022{\natexlab{a}})Yoachim, Jones, Eric H.~Neilsen,
  \& Ribeiro}]{yoachim2022b}
Yoachim, P., Jones, R.~L., Eric H.~Neilsen, J., \& Ribeiro, T.
  2022{\natexlab{a}}, {lsst-sims/sims\_featureScheduler\_runs2.2: Initial
  release}, v1.0.0,  Zenodo, \dodoi{10.5281/zenodo.7150784}

\bibitem[{Yoachim {et~al.}(2022{\natexlab{b}})Yoachim, Jones, Eric H.~Neilsen,
  Tiago, Carlin, pgris, Prisinzano, Bellm, Sick, lmptc, LI, nsabrams, Becker,
  Bricman, Bregeon, Kelley, \& Andreoni}]{yoachim2022}
Yoachim, P., Jones, L., Eric H.~Neilsen, J., {et~al.} 2022{\natexlab{b}},
  lsst/rubin\_sim: 0.12.1, 0.12.1,  Zenodo, \dodoi{10.5281/zenodo.7087823}

\bibitem[{Zonca {et~al.}(2019)Zonca, Singer, Lenz, Reinecke, Rosset, Hivon, \&
  Gorski}]{Zonca2019}
Zonca, A., Singer, L., Lenz, D., {et~al.} 2019, Journal of Open Source
  Software, 4, 1298, \dodoi{10.21105/joss.01298}

\end{thebibliography}
